---
title: "Shiny Tutorial"
author: "Sam Chavez"
date: "June 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First, we want to make sure we can share our shiny app with the world.

Step 1: Create an account on shinyapps.io (https://www.shinyapps.io/admin/#/signup)
  - Create an account name and then hit enter/return.
  
Step 2: Configure your account.  
  - Install rsconnect package in R
  - Click the "show secret" button in step 2 of shinyapps.io
  - Click the "copy to clipboard" button in step 2 of shinyapps.io
  - Copy the info in the popup and paste it into R & run
  - Load rsconnect library
  
Step 3: After you've created an awesome, original shiny app IN ITS OWN FOLDER
  - Set your working directory to your shiny app folder
  - Deploy your shiny app with rsconnect::deployApp()

```{r creating sharable shiny apps}
#install.packages('rsconnect')

##you should replace this with your own info from 
#rsconnect::setAccountInfo(name='schavez', token='F5D08BF684CEB0BAC3081F84BEBE4411', secret='lybcBWWniZw+Q9kL78zum9dgGzFvYEiSaUGGjNnW')
library(rsconnect)

#This step is for after you've made a shiny app
#setwd("~/UO/Spring 2018/Data Science/personal_site/shinythings/shinytest/")
#rsconnect::deployApp()

```




